Cauchy example

### 2020-05-06 src/s_cauchy.Rmd
updated cauchy distribution plot

Plot split-R* values for each parameterisation
```{r}
a_df <- tibble(nominal=r_star_nom,
               alt=r_star_alt,
               source="r_star") %>% 
  bind_rows(a_rhat_df) %>% 
  mutate(source=if_else(source=="r_star", "R*", "Rhat"))
g <-
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Parameterisation", labels=c("nominal", "alternative")) +
  xlab("Value") +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = "none") +
  facet_wrap(~source, scales = "free")
g
```

>>>>

Plot split-R* values for each parameterisation
```{r}
a_df <- tibble(nominal=r_star_nom,
               alt=r_star_alt,
               source="r_star") %>% 
  bind_rows(a_rhat_df) %>% 
  mutate(source=if_else(source=="r_star", "R*", "split-Rhat"))
g <-
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Parameterisation", labels=c("nominal", "alternative")) +
  xlab("Value") +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = "none") +
  facet_wrap(~source, scales = "free")
g
```
